Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2019-10-07 manuscript/manuscript.tex
changes
edits

\begin{center}
  \footnotesize
  \begin{tabular}{l c c c c c c}
    Study & Species & Selection & Replicates & Pop. Size & Gens. & Timepoints \\ 
  \hline
    \textcite{Kelly2019-dc}  & \emph{D. simulans} & lab & 3 & $\sim$1100 & 14 & 2 \\ \hline
    \textcite{Barghi2019-qy} & \emph{D. simulans} & lab & 10 & $\sim$1000 & 60 & 7 \\ \hline
    \textcite{Castro2019-uk} & \emph{M. musculus} & \begin{tabular}{c}tibiae length\\control\end{tabular} & \begin{tabular}{c}2\\1\end{tabular} &\begin{tabular}{c}32\\28\end{tabular}  & 20 & 2 \\
 \hline
  \end{tabular}
  \caption{\gc{A summary of the main selection studies we analyzed.}}
\end{center}

@@

% \vb{One concern is that these covariances reflect a few large-effect loci
%   rather than selection on a polygenic trait. Since our covariances are
%   essentially averages over loci, the covariance estimate can be strongly
%   affected by a single outlier region. To test whether large outlier regions
%   drive the genome-wide signal we see in the \textcite{Barghi2019-qy} data, we
%   calculate the covariances in 100kb windows along the genome (we refer to
%   these as windowed covariances throughout) and exclude the upper and lower
%   $\alpha$ tails to calculate the trimmed average windowed covariance. As
%   $\alpha$ increases to 0.5, the trimmed covariance converges to the median
%   windowed covariance (by the definition of the median; see Supplementary
%   Figure \ref{suppfig:barghi-trimmed-mean}). In other words, this median
%   windowed covariance is a measure of the genome-wide covariance robust to
%   large-effect loci; we find that the median windowed covariance $\cov(\Delta
%   p_0, \Delta p_{10})$ (pooling all replicates) is also significantly different
%   from zero, 0.0016 (0.95\% CIS [0.0015, 0.0017]).

%   XXX put a table median for all timepoints.
%  }

@@

Second, we reanalyzed the Longshanks selection experiment, which selected for
longer tibiae length relative to body size in mice, leading to a response to
selection of about 5 standard deviations over the course of twenty generations
\parencite{Castro2019-uk,Marchini2014-de}. This study includes two independent
selection lines, Longshanks 1 and 2 (LS1 and LS2), and an unselected control
line (Ctrl).  Consequently, this selection experiment offers a useful control
to test our between-replicate covariances: we expect to see positive
between-replicate covariance in the comparison between the two Longshanks
selection lines, but not between the two pairwise comparisons between the
control line and the two Longshanks lines. We find that this is the case (gray
confidence intervals in Figure \ref{fig:figure-2} C), with the two Longshanks
comparisons to the control line not being significantly different from zero,
while the comparison between the two Longshanks lines is statistically
significantly different from zero (CIs [0.013, 0.037]).

>>>>

\begin{table}
  \centering
  \footnotesize
  \centering
  \begin{tabular}{l c c c c c c}
    Study & Species & Selection & Replicates & Pop. Size & Gens. & Timepoints \\ 
  \hline
    \textcite{Kelly2019-dc}  & \emph{D. simulans} & lab & 3 & $\sim$1100 & 14 & 2 \\ \hline
    \textcite{Barghi2019-qy} & \emph{D. simulans} & lab & 10 & $\sim$1000 & 60 & 7 \\ \hline
    \textcite{Castro2019-uk} & \emph{M. musculus} & \begin{tabular}{c}tibiae length\\control\end{tabular} & \begin{tabular}{c}2\\1\end{tabular} &\begin{tabular}{c}32\\28\end{tabular}  & 20 & 2 \\
 \hline
  \end{tabular}
  \caption{A summary of the main selection studies we analyzed.}
\end{table}

@@

 \begin{table}
   \centering
   \footnotesize
   \centering
   \begin{tabular}{l c c c c c c}
     s & t & 5\% CI & median & 95\% CI & trimmed mean \\ \hline

     0 & 10 & 15.3 & 16.3 & 17.5 & 0.19 \\ \hline
     0 & 20 & 2.8 & 3.7 & 4.6 & 0.05 \\ \hline
     0 & 30 & 4.0 & 4.8 & 5.9 & 0.05 \\ \hline
     0 & 40 & -0.1 & 0.6 & 1.5 & 0.0 \\ \hline
     0 & 50 & -2.7 & -2.0 & -1.3 & -0.03 \\ \hline
     10 & 20 & 14.3 & 15.5 & 16.6 & 0.17 \\ \hline
     10 & 30 & 3.4 & 4.4 & 5.4 & 0.05 \\ \hline
     10 & 40 & 1.5 & 2.3 & 3.3 & 0.03 \\ \hline
     10 & 50 & -4.4 & -3.5 & -2.9 & -0.03 \\ \hline
     20 & 30 & 18.6 & 19.8 & 21.1 & 0.22 \\ \hline
     20 & 40 & 7.0 & 7.9 & 8.9 & 0.09 \\ \hline
     20 & 50 & 0.4 & 1.2 & 2.1 & 0.02 \\ \hline
     30 & 40 & 12.1 & 13.0 & 14.3 & 0.14 \\ \hline
     30 & 50 & -0.4 & 0.7 & 1.8 & 0.01 \\ \hline
     40 & 50 & 12.7 & 13.6 & 14.5 & 0.15 \\ \hline

   \end{tabular}

   \caption{Table of median of windowed covariance estimates ($\cov(\Delta p_s,
     \Delta p_t) \times 100$) between generations $t$ and $s$ and the trimmed
     mean windowed covariance which excludes the lower and upper 5\% windows
     with the highest covariance.}

 \end{table}

@@

Second, we reanalyzed the Longshanks selection experiment, which selected for
longer tibiae length relative to body size in mice, leading to a response to
selection of about 5 standard deviations over the course of twenty generations
\parencite{Marchini2014-de,Castro2019-uk}. This study includes two independent
selection lines, Longshanks 1 and 2 (LS1 and LS2), and an unselected control
line (Ctrl).  Consequently, this selection experiment offers a useful control
to test our between-replicate covariances: we expect to see positive
between-replicate covariance in the comparison between the two Longshanks
selection lines, but not between the two pairwise comparisons between the
control line and the two Longshanks lines. We find that this is the case (gray
confidence intervals in Figure \ref{fig:figure-2} C), with the two Longshanks
comparisons to the control line not being significantly different from zero,
while the comparison between the two Longshanks lines is statistically
significantly different from zero (CIs [0.013, 0.037]).
